### 2019-12-22 README.Rmd
Update readme - figures

The goal of zonebuilder is to break up large regions into manageable zones for research and applied transport planning, to support the global transition away from fossil fuels in the transport sector, and towards more healthy modes of transport like walking, cycling and renewable electricity-powered public transport.

>>>>

The goal of zonebuilder is to break up large geographic regions such as cities into manageable zones.
Zoning systems are important in many fields, including transport planning, where we hope to use the zones generated by `zonebuilder` to build the evidence base needed to enable uptake of healthy modes of transport like walking, cycling and renewable electricity-powered public transport. See its website at [zonebuilders.github.io/zonebuilder](https://zonebuilders.github.io/zonebuilder/).
